---
title: "RBasicsQuiz"
output: html_document
date: "2025-05-29"
---
# Variable naming: case-sensitive, can't start with numbers, there are reserved words, and they CAN contain underscores and periods

# typeof() returns a low-level type - the primitive type, class() returns a high-level abstraction - more about behavior
```{r}
a <- 10L # Added L makes this an integer (for both class and typeof)
b <- 10 # Numeric for class, double for typeof
cat(class(a), typeof(b), sep = ", ")

x <- "123"
y <- as.numeric(x) # Numeric means a double by default
typeof(y)
```

# Can convert between types using as.type()
```{r}
x <- "TRUE"
y <- as.logical(x) # "TRUE" -> TRUE
z <- as.numeric(y) # TRUE -> 1
print(z)

a <- 0
as.logical(a + 2 - 2) # 0 -> FALSE

as.numeric("Hello") # Can't convert -> NA
```

# Short-circuit logical operators: &&, || evaluate only the first element of each vector while element-wise logical operators: &, | evaluate all elements

# Any() and all()
```{r}
x <- c(TRUE, TRUE, FALSE)
any(!x) # Are any of the values false? -> yes

x2 <- c(1, 2, 3)
y <- c(3, 2, 1)
z <- x > y 
all(z) # Are all values true? -> no
```

# Cat() creates a vector
```{r}
x <- TRUE
y <- FALSE
z <- NA

cat(x & y, y | z, !z, "\n")
```
